Making Soup: Preparing and Validating Molecular Simulations of the Bacterial Cytoplasm

### 2019-10-10 paper/virtual_cytoplasm_v2.tex
Review again

Three crowders (TufA, MetE and IcdA) displayed greater deviation from
their crystallographic structure in the cytoplasm model when compared
to the dilute condition, indicating that there was some degree of
local unfolding
(Fig.~\ref{fig:structural_integrity_chain}A). Interestingly, oligomers
were marginally less stable {\color{blue} in the cytoplasm model} {\bf THAN WHAT? Monomers?} {\color{blue} oligomers in the cytoplasm were marginally less stable than oligomers in the dillute condition. Added "in the cytoplasm model" to the text.}
(Fig.~\ref{fig:structural_integrity_chain}B) and the flexibility
profiles calculated considering the C$\upalpha$ for each chain of the
elements of our cytoplasm model show that, in the crowded condition,
most of the proteins (TufA, MetE, AhpC, CspC and Ppa) are slightly
more flexible than in the dilute condition (Fig.~\ref{fig:rmsf}). This
is in agreement with previous simulations~\cite{Feig2011} and
experiment~\cite{miklos2011,Wang2012b} showing that crowders can
destabilize the native structure of proteins due to the numerous
unspecific short-lived interactions that are formed between them in a
crowded environment. A study of protein properties at increasing
concentration showed only few interactions between proteins of the
same type, however~\cite{Bashardanesh2019a}. {\color{blue} We highlight that there are no specific interactions between the proteins that were used in our cytoplasm model.} {\bf do we expect specific interactions between the proteins in our cyto model? In that case write that with references, otherwise write that there are no known specific interactions between these proteins.} {\color{blue} The only specific interaction we antecipate between the components of the soup is that TufA interacts with tRNA (PDB ID 1TTT is an example of such complex). However, since we are ignoring tRNA in our analyses, I did't mention it. PS: I checked and the TufA-tRNA complex is not present in the last frames of our replicas.}

>>>>

Three crowders (TufA, MetE and IcdA) displayed greater deviation from
their crystallographic structure in the cytoplasm model when compared
to the dilute condition, indicating that there was some degree of
local unfolding
(Fig.~\ref{fig:structural_integrity_chain}A). Interestingly, oligomers
were marginally less stable {\color{blue} in the cytoplasm model} {\bf THAN WHAT? Monomers?} {\color{blue} oligomers in the cytoplasm were marginally less stable than oligomers in the dillute condition. Added "in the cytoplasm model" to the text.}
(Fig.~\ref{fig:structural_integrity_chain}B) and the flexibility
profiles calculated considering the C$\upalpha$ for each chain of the
elements of our cytoplasm model show that, in the crowded condition,
most of the proteins (TufA, MetE, AhpC, CspC and Ppa) are more flexible than in the dilute condition (Fig.~\ref{fig:rmsf}). This
is in agreement with previous simulations~\cite{Feig2011} and
experiment~\cite{miklos2011,Wang2012b} showing that crowders can
destabilize the native structure of proteins due to the numerous
unspecific short-lived interactions that are formed between them in a
crowded environment. A study of protein properties at increasing
concentration showed only few interactions between proteins of the
same type~\cite{Bashardanesh2019a}. {\color{blue} We highlight that there are no specific interactions described between the proteins that were used in our cytoplasm model.} {\bf do we expect specific interactions between the proteins in our cyto model? In that case write that with references, otherwise write that there are no known specific interactions between these proteins.} {\color{blue} The only specific interaction we antecipate between the components of the soup is that TufA interacts with tRNA (PDB ID 1TTT is an example of such complex). However, since we are ignoring tRNA in our analyses, I did't mention it. PS: I checked and the TufA-tRNA complex is not present in the last frames of our replicas.}
